\documentclass[10pt, a4paper]{article}
%\usepackage{geometry}
\usepackage[inner=2.5cm,outer=2.5cm,top=2.5cm,bottom=2.5cm]{geometry}
\pagestyle{empty}
\usepackage{graphicx}
\usepackage{fancyhdr, lastpage, bbding, pmboxdraw}
\usepackage[usenames,dvipsnames]{color}
\usepackage[colorlinks,pagebackref,pdfusetitle,urlcolor=darkblue,citecolor=darkblue,linkcolor=darkred,bookmarksnumbered,plainpages=false]{hyperref}
\usepackage{amsfonts}
\usepackage{listings}
\usepackage{caption}
\usepackage{placeins}
\DeclareCaptionFont{white}{\color{white}}
\DeclareCaptionFormat{listing}{\colorbox{gray}{\parbox{\textwidth}{#1#2#3}}}
\captionsetup[lstlisting]{format=listing,labelfont=white,textfont=white}
\usepackage{verbatim} % used to display code
\usepackage{fancyvrb}
\usepackage{acronym}
\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{pgfplots}
\VerbatimFootnotes


%Set up the headers
\pagestyle{fancyplain}
\fancyhf{}
\lhead{ \fancyplain{}{\classNum} }
\chead{ \fancyplain{}{\topic} }
\rhead{ \fancyplain{}{Dr. Hannay} }
%\rfoot{\fancyplain{}{page \thepage\ of \pageref{LastPage}}}
\fancyfoot[RO, LE] {page \thepage\ of \pageref{LastPage} }
\thispagestyle{plain}


%Set up the theorem enviroment
\newtheoremstyle{break}
  {\topsep}{\topsep}%
  {\itshape}{}%
  {\bfseries}{}%
  {\newline}{}%
\theoremstyle{break}

\newtheorem{theorem}{Theorem}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{conj}[theorem]{Conjecture}
\newtheorem{defn}[theorem]{\underline{Definition:}}

%Set up custom commands
\renewcommand\thesection{\Roman{section}.}
%exercise command \ex{question}{space times 0.5 inches}
\newcommand{\question}[3]     {
 #1 (\textbf{#2 points}) \newline 
\newcount\Scount
\Scount=0
\loop\vspace*{0.5in}\par\goodbreak\advance\Scount by 1 \ifnum\Scount< #3 \repeat
}%Makes an exercise with space left for the students to write the answer
\newcommand{\makesol}[1]     {
\newcount\Scount
\Scount=0
\loop\vspace*{0.5in}\par\goodbreak\advance\Scount by 1 \ifnum\Scount< #1 \repeat
}%Makes an exercise with space left for the students to write the answer

\newcommand{\fpquestion}[3]     {
 #1 (\textbf{#2 points}) \newline 
\newpage
}%Makes an exercise with space left for the students to write the answer

%Calculus specific shorthands
\newcommand{\dlim}{\lim_{h\rightarrow0}}



%Make ShortHands for quick updates
\renewcommand{\thefootnote}{\fnsymbol{footnote}}
\newcommand{\topic}{{Exam IV}}
\newcommand{\classNum}{{MATH 3324}}
\newcommand{\prob}{{\mathbb{P}}}

\definecolor{OliveGreen}{cmyk}{0.64,0,0.95,0.40}
\definecolor{CadetBlue}{cmyk}{0.62,0.57,0.23,0}
\definecolor{lightlightgray}{gray}{0.93}
\definecolor{darkblue}{rgb}{0,0,.6}
\definecolor{darkred}{rgb}{.7,0,0}
\definecolor{darkgreen}{rgb}{0,.6,0}
\definecolor{red}{rgb}{.98,0,0}


\lstset{
%language=bash,                          % Code langugage
basicstyle=\ttfamily,                   % Code font, Examples: \footnotesize, \ttfamily
keywordstyle=\color{OliveGreen},        % Keywords font ('*' = uppercase)
commentstyle=\color{gray},              % Comments font
numbers=left,                           % Line nums position
numberstyle=\tiny,                      % Line-numbers fonts
stepnumber=1,                           % Step between two line-numbers
numbersep=5pt,                          % How far are line-numbers from code
backgroundcolor=\color{lightlightgray}, % Choose background color
frame=none,                             % A frame around the code
tabsize=2,                              % Default tab size
captionpos=t,                           % Caption-position = bottom
breaklines=true,                        % Automatic line breaking?
breakatwhitespace=false,                % Automatic breaks only at whitespace?
showspaces=false,                       % Dont make spaces visible
showtabs=false,                         % Dont make tabls visible
columns=flexible,                       % Column format
morekeywords={__global__, __device__},  % CUDA specific keywords
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
\begin{center}
{\large \textsc{\underline{MATH 3312: Quiz II}}}
\vspace{0.125in}
\end{center}
\underline{Directions:} \\
Complete this exam without consulting with \underline{anyone} else for help answering the questions (electronically, in person, etc). You may use your notes, the notes on S1 and your textbook. Additionally, you are allowed to use numerical computing software to aid you in answering the questions. \textbf{You must show all of your work. If you use numerical software then write in the command you used. Failure to show all of the steps used to obtain your solution will result in NO points being awarded for that question. } 
\noindent The quiz must be turned in by the beginning of class on Weds 4/18/2017. If you want to turn it in early make sure you hand it to me in person (don't put it in the box outside my office). Good luck! \\
\noindent\rule{15cm}{0.4pt}

\vspace{0.25in}

\begin{enumerate}
\item Find a basis for the nullspace of the following matrix:
\begin{equation}
A=
\begin{bmatrix}
1 & 2 & 3 &4 \\
1 &0 & 1 &4 
\end{bmatrix}
\nonumber
\end{equation}
\item Create a matrix $A$ where the nullspace $N(A)$ is all combinations of $\vec{n}=\langle 1, 2 \rangle$.
\item  Find the dimensions of the four fundamental subspaces for the following matrix:
\begin{equation}
A=
\begin{bmatrix}
1 & -1 & 2 &1 & 0 \\
1 & 1 & 0 & 0 & 0\\
1 & -5 & 6 & 3 & 0\\
-4 & 0 &-4 & -2 & 0
\end{bmatrix}
\end{equation}
\item If $AB=0$ then the columns of $B$ are the \underline{\hspace{1cm}} of $A$. The rows of $A$ are in the  \underline{\hspace{1cm}} of $B$. If $AB=0$ explain why it is not possible for $A$ and $B$ to be $3 \times 3$ matrices of rank 2. 
\item Is it true that the product $A^TA$ has the same nullspace as $A$? Prove your answer (show for general matrices) or find a counterexample. 
\item Find the least squares solution for the best fit line for the points $(0,1), (1,3), (2,6),(3,9),(4,10)$. 
\item Find the projection of the vector $\vec{b}=\langle 1,2,3 \rangle$ onto the space spanned by $\vec{a}=\langle 1,1,-1 \rangle$. Show that the error vector is orthogonal to $\vec{a}$. 
\item Let $P$ be a $n \times n$ projection matrix. Show that the nullspace of the complementary projection matrix $P_c=\mathbb{I}-P$ is the column space of $P$. 
\item Find the \underline{complete solution} to the following system:
$$
\begin{bmatrix}
1 & 0 & -1 \\
2 & 1 & 1
\end{bmatrix}
\begin{bmatrix}
x_1 \\
x_2 \\
x_3
\end{bmatrix}
=
\begin{bmatrix}
-6 \\
3
\end{bmatrix} 
$$
% -2,3,4
\item Is the following set of vectors a basis for $\mathbb{R}^3$?
\begin{align}
v_1=\begin{bmatrix} 1 \\ 0 \\1 \end{bmatrix} \qquad v_2=\begin{bmatrix} 1 \\ 1 \\ -1 \end{bmatrix} \qquad v_3=\begin{bmatrix} 6 \\ -12\\ 4 \end{bmatrix}
\end{align}
\end{enumerate}

























\end{document}